Impact ionization processes in driven Mott insulating layer: influence of fermion baths and phonons

### 2022-07-21 figures_Paper1/test_old/spec_filling_mu1_v_0.4_0.8_E4_O_11.5_eph.tex
Added sources for figures

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
};

>>>>

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4E4_O11.5.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.4phE4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4phE4_O11.5.dat' u 1:3 w l;
};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.8E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8E4_O11.5.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8phE4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8phE4_O11.5.dat' u 1:3 w l;
};

### 2022-07-21 figures_Paper1/test_old/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
Added sources for figures

\begin{groupplot}[
group style={
group size=2 by 1,
xticklabels at=edge bottom,  
yticklabels at=edge left,
%vertical sep=10pt,
horizontal sep=20pt
}, 
minor tick num=1, 
width=0.6\textwidth,
height=0.6\textwidth    
]

@@

>>>>

\begin{groupplot}[
group style={
group size=2 by 2,
xticklabels at=edge bottom,  
yticklabels at=edge left,
%vertical sep=10pt,
horizontal sep=20pt
}, 
minor tick num=1, 
width=0.6\textwidth,
height=0.6\textwidth    
]

@@

%  3° figure

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$\Omega=5$};
\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$\Omega=11$};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(c)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};

%  4° figure

\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt}
\addlegendentry{$\Omega=5$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt}
\addlegendentry{$\Omega=11$};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(d)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};

### 2022-07-21 figures_Paper1/test_old/spec_filling_mu1_v_0.4_0.8_O_5_11_eph.tex
Added sources for figures

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega/t^{*}$},
ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0, 
    /tikz/.cd}
]

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=5$};

@@

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=11$};

@@

\nextgroupplot[
xmin=-15.,    
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega/t^{*}$},
ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$\Omega=5$};
\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$\Omega=11$};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(c)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};

>>>>

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
% grid=both,
% xlabel={$\omega/t^{*}$},
ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0, 
    /tikz/.cd}
]

% \addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
% \addlegendentry{$el$};
% \addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
% \addlegendentry{$el+ph$};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O5.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.4O5ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O5ph.dat' u 1:3 w l;
};

% VERTICAL LINES + ARROWS MARKING THEIR DISTANCE

\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(-2.5, 0.0) (-2.5, 0.09)};
\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(2.5, 0.0) (2.5, 0.09)};
% \draw [stealth-stealth,thick,color=gray](-2.5, 0.03) -- (2.5, 0.03);

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};

@@

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
% grid=both,
% xlabel={$\omega/t^{*}$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$el$};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{$el+ph$};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O5.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8O5ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O5ph.dat' u 1:3 w l;
};

% VERTICAL LINES + ARROWS MARKING THEIR DISTANCE

\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(-2.5, 0.0) (-2.5, 0.09)};
\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(2.5, 0.0) (2.5, 0.09)};
% \draw [stealth-stealth,thick,color=gray](-2.5, 0.03) -- (2.5, 0.03);

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};

@@

\nextgroupplot[
xmin=-15.,    
xmax=15., 
ymin=-0.01, 
ymax=0.01,   
minor tick num=1, 
% grid=both, 
xlabel={$\omega/t^{*}$},
ylabel={$j(\omega)$},
legend style={at={(axis cs:0,0.011)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={-0.01,0.00,0.01},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$el$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$el+ph$};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './J00_omega_hyb0.4O5.dat' u 1:2 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './J00_omega_hyb0.4O5ph.dat' u 1:2 w l;
};

% VERTICAL LINES + ARROWS MARKING THEIR DISTANCE

\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(-2.5, 0.0) (-2.5, 0.01)};
\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(2.5, 0.0) (2.5, 0.01)};
\draw [stealth-stealth,thick,color=gray](-2.5, 0.005) -- (2.5, 0.005);

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.008) {\bfseries(c)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.008) {$v=0.4$};
